Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-15 examples_C.tex
+

@@

    /*... entry value updates:*/

@@

    /*... now we know that entry is initialized, so we satisfy the condition to access children list */

@@

  /*...  Code after conditional continued in Figure (*\ref{fig:p2v}*)*/

>>>>

@return next: return a virtual pointer to the descendant tree

@@

    /*Entry value updates:*/

@@

    /*Now we know that entry is initialized, so we satisfy the condition to access children list */

@@

  /*Physical to virtual address mapping (*\ref{fig:p2v}*)*/
